\msusection{Installation}\label{sec:install}
\msusubsection{System Requirements}
YCweather is a Windows based program that was compiled using MATLAB 2008b (\href{http://www.mathworks.com}{The Mathworks, Inc.}) and requires MATLAB Component Runtime 7.9.  YCweather was designed to automatically update the software as well as the weather data files.  Thus, it is recommended that when using YCweather that the computer be connected to the Internet.  However, the Internet is not a requirement to run YCweather and for this case the automatic data download option should be turned off, see the Section \ref{sec:pref} for details.

\msusubsection{Installing YCweather}\label{sec:install}
YCweather is available for download from the website of the Subzero Science and Engineering Research Facility\footnote{\href{http://www.coe.montana.edu/ce/subzero/snow/}{\nolinkurl{www.coe.montana.edu/ce/subzero/snow}}} at \href{http://www.montana.edu}{Montana State University}.  To install the software the following steps must be followed.

\begin{enumerate}
\item Download the MATLAB Compiler Runtime (\href{http://www.coe.montana.edu/ce/subzero/snow/MCRInstaller.exe}{MCRinstaller.exe}) software, this is the background program necessary to run YCweather: \href{http://www.coe.montana.edu/ce/subzero/snow/MCRInstaller.exe}{\nolinkurl{www.coe.montana.edu/ce/subzero/snow/MCRInstaller.exe}}.
\item Download the YCweather installer software package, \href{http://www.coe.montana.edu/ce/subzero/snow/YCinstaller.exe}{YCinstaller.exe}: \href{http://www.coe.montana.edu/ce/subzero/snow/YCinstaller.exe}{\nolinkurl{www.coe.montana.edu/ce/subzero/snow/YCinstaller.exe}}.
\item Execute the MCRinstaller.exe file, using the default settings for this program is recommended.
\item Execute the YCinstaller.exe and follow the instructions, it installs similar to most Windows programs.
\item When the installation process is complete, YCweather may be run by using the YCweather.exe file located in the created program directory. 
\end{enumerate}


\msusubsection{Updates}
YCweather is a software package that is under development, as such updates will be available periodically.  When an update is available YCweather will provide the user with a prompt, giving the user the option to update YCweather.  It is strongly recommend that if a new version is available that it be installed.  The installation of the update will occur automatically.  Note, if the computer running YCweather does not have Internet access the automatic update warnings will not be received.  In this case, the user should periodically check the download page for a newer version of the software. To install an updated version, simply download the file and install it as explained in the installation instructions above.  When installing allow the new version to overwrite the old files, no data will be lost during this process.  MCRinstaller.exe only needs to be installed with the initial installation.

